Tables/Graphs for Article

### 2017-11-25 article submission/draft1.Rnw
added draft in Sweave format

\documentclass[12pt]{article}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text

% Sets margins to 1 in
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

%-----------------------------------------------------------------------------------
\title{Rough Draft}
\author{Lisa Oshita}
\date{}
%-----------------------------------------------------------------------------------

\begin{document}

\maketitle

\section{Abstract}

Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. Forums can cover a broad range of topics, like \textit{Yahoo! Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. As such, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

\section{Introduction}

@@

    As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions pertaining to over 9,000 devices with over 100,000 solutions. Questions range from broken devices like jammed zippers to shattered iPhone screens. As many rely on this forum for help with repairs, it is important that users receive timely answers. Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.

    However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated. As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.

\section{Related Work}

@@

\section{Materials}

@@

\section{Methods}

    Questions analyzed were restricted to those posted in English (97\% of the full data). The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

Survival was defined as the event that a question did not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method (cite), which adjusts to the presence of right-censored, or unanswered questions. This method factors in the number of questions that have not been answered on each ordered interval of complete answer times. Estimates of survival probablity are the products of all probabilities up to that interval's time (redo this). From these estimates, survival curves were constructed to examine the survival experience of questions, and mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied. Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.

@@

\section{Results}

  Of 7,760 questions, 4,651 (63.8\%) received an answer by the download date. The shortest answer time was 0.01 hours. The longest was 2159.02 hrs (89.96 days). Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer. Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table 1 provides additional percentiles of survival time.

@@

\section{Discussion}

@@

\section{Conclusion}

@@

\section{Acknowledgement}

>>>>

\documentclass{article}

\begin{document}
\SweaveOpts{concordance=TRUE}

<< echo = FALSE >>=
# setting up model
dir <- file.path(getwd(),"data")
x <- read.csv(file.path(dir, "dat.csv"))

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)

# -------------------------------------------------------------------------------
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
@

\section*{Abstract}

Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. Forums can cover a broad range of topics, like \textit{Yahoo! Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. As such, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

\section*{Introduction}

@@

As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions pertaining to over 9,000 devices with over 100,000 solutions. Questions range from broken devices like jammed zippers to shattered iPhone screens. As many rely on this forum for help with repairs, it is important that users receive timely answers. Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved. 
However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated. As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.

\section*{Related Work}

@@

\section*{Materials}

@@

\section*{Methods}

Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data). The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

Survival was defined as the event that a question did not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions (cite). From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied. Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.

@@

<<include = FALSE>>=
answered <- sum(x$answered)
percentans <- round((answered / nrow(x)) * 100, 1) 
shortest <- round(min(x$time_until_answer) * 60, 2) 
longest <- round(max(x$time_until_answer), 2)
longest_d <- round(longest / 24, 2) 
@

\section*{Results}

  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest answer time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

\begin{figure}[h!]
  \includegraphics[scale=1]{times_dist.pdf}
  \caption{Distribution of answer times}
  \label{fig:answertimes}
\end{figure}

\begin{figure}[h!]
  \includegraphics[scale=1]{kmcurve.pdf}
  \caption{Kaplan-Meier curve for all questions}
  \label{fig:kmcurve}
\end{figure}

<<include = FALSE>>=
surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
stats <- summary(KM)$table
mean <- round(unname(stats[5]), 2) 
median <- round(unname(stats[7]), 2)
@

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Fri Nov 24 17:16:56 2017
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
  Percent \\ Answered & Time (hours) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\label{table:quantiles}
\end{table}

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table ~\ref{table:quantiles} provides additional percentiles of survival time.

@@

\section*{Discussion}

@@

\section*{Conclusion}

@@

\section*{Acknowledgement}

### 2017-11-25 article submission/draft1.tex
added draft in Sweave format

\begin{document}
\SweaveOpts{concordance=TRUE}

<< echo = FALSE >>=
# setting up model
dir <- file.path(getwd(),"data")
x <- read.csv(file.path(dir, "dat.csv"))

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)

# -------------------------------------------------------------------------------
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
@

@@

Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. Forums can cover a broad range of topics, like \textit{Yahoo! Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. As such, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data). The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied. Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.

@@

<<include = FALSE>>=
answered <- sum(x$answered)
percentans <- round((answered / nrow(x)) * 100, 1) 
shortest <- round(min(x$time_until_answer) * 60, 2) 
longest <- round(max(x$time_until_answer), 2)
longest_d <- round(longest / 24, 2) 
@

@@

  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest answer time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

@@

<<include = FALSE>>=
surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
stats <- summary(KM)$table
mean <- round(unname(stats[5]), 2) 
median <- round(unname(stats[7]), 2)
@

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table ~\ref{table:quantiles} provides additional percentiles of survival time.

>>>>

\usepackage{Sweave}
\begin{document}
\input{draft1-concordance}

@@

Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. Forums can cover a broad range of topics, like \textit{Yahoo! Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. As such, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

Questions analyzed were restricted to those posted in English (7760 questions, 97\% of the full data). The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6208 questions, and each test set contained 1552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied. Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.

@@

\begin{Schunk}
\begin{Sinput}
> answered <- sum(x$answered)
> percentans <- round((answered / nrow(x)) * 100, 1) 
> shortest <- round(min(x$time_until_answer) * 60, 2) 
> longest <- round(max(x$time_until_answer), 2)
> longest_d <- round(longest / 24, 2) 
\end{Sinput}
\end{Schunk}

@@

  Of 7760 questions, 4951 (63.8}\%) received an answer by the download date. The shortest answer time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

@@

\begin{Schunk}
\begin{Sinput}
> surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
> KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
> stats <- summary(KM)$table
> mean <- round(unname(stats[5]), 2) 
> median <- round(unname(stats[7]), 2)
\end{Sinput}
\end{Schunk}

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table ~\ref{table:quantiles} provides additional percentiles of survival time.

### 2017-11-25 article submission/graphics.Rmd
added draft in Sweave format

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
list <- oshitar::variable_setup(out)
x <- list[[1]]
```

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + 
                   rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
```

@@

@@

trains <- list(train1, train2, train3, train4, train5)
trains <- purrr::map(trains, ~as.data.frame(.))
tests <- list(test1, test2, test3, test4, test5)
tests <- purrr::map(tests, ~as.data.frame(.))

# ------------------------------------------
# without splines
vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + avg_tag_score + text_length + device_length + avg_tag_length + newline_ratio"

@@

# ------------------------------------------
# with splines
vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(text_length, 4) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"

@@

# residuals

```{r}
final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                  contain_unanswered + contain_answered + title_questionmark + 
                  text_contain_punct + text_all_lower + update + prior_effort + weekday + 
                  sqrt(avg_tag_score) + rcs(text_length, 4) + rcs(device_length, 5) + 
                  rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                  data = x, x = TRUE, 
                  y = TRUE, surv = TRUE)
final

x$mart <- residuals(final, type = "martingale")

@@

plotm <- function(var) {
  ggplot(x, aes(x = x[[var]], y = mart)) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Martingale Residuals for", var)) + 
    scale_x_continuous(var)
}
plotm("avg_tag_score")
plotm("text_length")
plotm("device_length")
plotm("avg_tag_length")
plotm("newline_ratio")

```

@@

```{r}
# model statistics + parameters
# figure out how to get p-values 
parameterdf <- data.frame(variable = names(final$coefficients),
                          coefficients = round(unname(final$coefficients), 3))
parameterdf

modelstats <- data.frame(statistic = names(final$stats), 
                         value = round(unname(final$stats), 3))
modelstats

# ------------------------------------------
# cross-validation metrics 
x$predictions <- exp(predict(final, type = "lp"))

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(metric, k = 2) # 83125.55

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics 
```

>>>>

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
list <- oshitar::variable_setup(out)
x <- list[[1]]
library(rms); library(survival); library(ggplot2)
```

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 3) + rcs(log10(text_length), 3) +
                   rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
model
```

@@

```{r}
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]

pvalues <- data.frame(variable = character(), 
                      pvalue = numeric())

# function to get summary of cox model + append pvalue of variable from loglik test to df
# ---------------------------------------------------------------------------------------
get_pvalue <- function(variable, factor = FALSE) {
  if (factor == FALSE){
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ train1[[variable]], data = train1)
  } else {
    coxmodel <- coxph(Surv(time_until_answer, answered) ~ as.factor(train1[[variable]]), data = train1)
  }
  summary <- summary(coxmodel)
  df <- data.frame(variable = variable, 
                   pvalue = unname(summary$logtest[[3]]))
  pvalues <- rbind(pvalues, df)
  return(pvalues)
}
# ---------------------------------------------------------------------------------------

pvalues <- get_pvalue("new_category")
pvalues <- get_pvalue("new_user")
pvalues <- get_pvalue("title_questionmark")
pvalues <- get_pvalue("text_contain_punct")
pvalues <- get_pvalue("weekday")
pvalues <- get_pvalue("text_length")
pvalues <- get_pvalue("device_length")
train1$logdevice <- log10(train1$device_length)
train1$sqrtdevice <- sqrt(train1$device_length)
pvalues <- get_pvalue("sqrtdevice")
pvalues <- get_pvalue("text_all_lower")
pvalues <- get_pvalue("prior_effort")
pvalues <- get_pvalue("update")
pvalues <- get_pvalue("newline_ratio")
train1$sqrtnewline <- sqrt(train1$newline_ratio)
pvalues <- get_pvalue("sqrtnewline")
train1$sqrt <- sqrt(train1$avg_tag_length)
pvalues <- get_pvalue("sqrt")
pvalues <- get_pvalue("avg_tag_score")
pvalues <- get_pvalue("contain_unanswered")
pvalues <- get_pvalue("contain_answered")
train1$logtext <- log10(train1$text_length)
pvalues <- get_pvalue("logtext")
options(scipen=999)
pvalues <- pvalues %>% arrange(pvalue)
pvalues

rms::cph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
rms::cph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = x)
rms::cph(Surv(time_until_answer, answered) ~ avg_tag_length, data = train1)

rms::cph(Surv(time_until_answer, answered) ~ sqrt(newline_ratio), data = train1)

ggplot(train1, aes(x = logtext)) + 
  geom_histogram()
ggplot(train1, aes(x = text_length)) + geom_histogram()
ggplot(train1, aes(x = log10(device_length))) + geom_histogram()
ggplot(train1, aes(x = sqrt(newline_ratio))) + geom_histogram()
```

@@

# ------------------------------------------
# without splines
vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + text_length + device_length + sqrt(avg_tag_length) + newline_ratio"

@@

# ------------------------------------------
# with splines
vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 3) + rcs(sqrt(avg_tag_length), 3) + rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3)"

@@

```{r}
avg_results1
```

### residuals

```{r}
x$mart <- residuals(model, type = "martingale")

@@

plotm <- function(var) {
  ggplot(x, aes(x = x[[var]], y = mart)) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Martingale Residuals for", var)) + 
    scale_x_continuous(var)
}

x$sqrt_length <- sqrt(x$avg_tag_length)
x$sqrt_score <- sqrt(x$avg_tag_score)

plotm("sqrt_score")
plotm("text_length")
plotm("device_length")
plotm("sqrt_length")
plotm("newline_ratio")
```

@@

```{r}
# model statistics + parameters
# figure out how to get p-values 
parameterdf <- data.frame(variable = names(model$coefficients),
                          coefficients = round(unname(model$coefficients), 3))
parameterdf

modelstats <- data.frame(statistic = names(model$stats), 
                         value = round(unname(model$stats), 3))
modelstats

# ------------------------------------------
# cross-validation metrics 
x$predictions <- exp(predict(model, type = "lp"))

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(metric, k = 2) # 83124.21

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics

# ------------------------------------------
ph <- cox.zph(model)
ph_test <- data.frame(predictors = rownames(ph$table), ph$table)
rownames(ph_test) = NULL
ph_test <- ph_test %>% arrange(p) 
ph_test
```

```{r}
final_metrics
```
